%-------------------------
% Janpreet Singh Resume
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[document]{ragged2e}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubSubItem}[1]{
  \item\small{
    {#1}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
        \small #3 & \small #4 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small #1 & \small #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://janpreet.com/}{\Large Janpreet Singh}} & Email: \href{mailto:hire@janpreet.com}{hire@janpreet.com}\\
  \href{https://janpreet.com/}{https://janpreet.com} & Phone: on-request \\
\end{tabular*}

\justifying

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Science in Information Systems}{Jan. 2018}    
      {Marist College, 3.34}{Poughkeepsie, NY}
    \resumeSubheading
      {Bachelor of Technology in Electronics and Communications Engineering}{May. 2012}    
      {Guru Gobind Singh Indraprastha University, 3.33}{New Delhi, India}
  \resumeSubHeadingListEnd

\section{Tech Stack}
  {Azure, AWS, Kubernetes, Docker, Ansible, Splunk, Datadog, Terraform, Google Cloud, Hashicorp Vault, Consul, Rancher, MongoDB Atlas,
  Jenkins, Linux, Bash, Python}
 
\section{Summary}
  {DevOps Engineer interested in architecting and deploying high-quality automation, particularly to save operational
  cost, and ensure resiliency, efficieny and high-availability of systems. Love to teach and 
  mentor people. Looking forward to grow and mature as a DevOps Leader.}
 

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Unqork}{Remote, NYC}
      {DevOps Engineer}{Nov 2021 - Present}
      \resumeItemListStart
        \resumeSubSubItem
          {Part of 24x7x365 on-call DevOps roation (Agile) supporting upgrades and releases of customer environments and infrastrucutre.}
        \resumeSubSubItem
          {Architecured and delivered contractual cross-function platform features using AWS while ensuring positive developers experience}
        \resumeSubSubItem
          {Successfully moved internal DevOps tools and hundreds of multi-cloud customer environments to kubernetes using Ansible and Terraform.}                                     
      \resumeItemListEnd 

    \resumeSubheading
      {Caissa LLC (Merged with Burgiss)}{Remote, NYC}
      {DevOps Engineer}{May 2021 - Nov 2021}
      \resumeItemListStart
        \resumeSubSubItem
          {Introduced and successfully setup (architectured and deployed) Terraform managed VDI, DR AKS and AWS MWAA tied to Azure AD.
          Also setup git mirror between Azure repos and AWS CodeCommit for disaster-recovery.}
        \resumeSubSubItem
          {Setup on-demand build and release agents in Kubernetes to eliminate Azure pipelines build queues.}       
        \resumeSubSubItem
          {Automated manual Windows service releases using Ansible as one of the very first tasks at the new role.}                                     
      \resumeItemListEnd  

    \resumeSubheading
      {Globalfoundries}{Malta, NY}
      {Sr. Mfg Systems Engineer, SRE}{July 2020 - May 2021}
      \resumeItemListStart     
        \resumeSubSubItem
          {Evangelized and implemented SRE best practices by utilizing automated deployment procedures 
          using BitBucket, Jenkins and Ansible, for faster deployments and roll-backs.}
        \resumeSubSubItem
          {Disposable Kubernetes cluster POC; created using Terraform and Google Cloud Platform. 
          Sample Maven and Python applications built using Jenkins Docker Cloud and deployed using Helm 
          to demonstrate the DevOps model. Wrote a custom Terraform module `cluster-kubeconfig` 
          to solve GKE module`s lack of kubeconfig generation.}          
      \resumeItemListEnd
      
    \resumeSubSubheading
      {Mfg Systems Engineer}{Jan 2019 - June 2020}
      \resumeItemListStart
        \resumeSubSubItem
          {Ensured 99.95\% uptime of critical applications in a 24x7x365 environment by 
          utilizing a comprehensive monitoring strategy in Splunk to automate detection 
          and trigger response to incidents and outages. Reduced MTTR where automation 
          was not possible by providing effective runbooks to Level 1 Support.}
        \resumeSubSubItem
          {Developed, tested, and implemented a Java application to eliminate repetitive data entry 
          tasks that saved \$9k worth of labor hours annually. Used Hibernate to interact with 
          Oracle DB and Selenium libraries for automation where API access was not possible. 
          Packaged the app using Maven \& Docker and created a CI/CD pipeline to execute testing 
          and deployment using Jenkins.} 
      \resumeItemListEnd

    \resumeSubSubheading
      {AMHS Factory Automation Engineer}{Jan 2018 - Dec 2018}

    \resumeSubSubheading
      {AMHS Co-op Engineer}{May 2017 - Dec 2017}

  \resumeSubHeadingListEnd

% \section{Projects}
%   \resumeSubHeadingListStart
%     \resumeSubSubItem
%       {Raspberry Pi based highly-available Kubernetes cluster; deployed the hard way using only Ansible. 
%       Inspired by Kelsey Hightower. I created Roles for provisioning certs and bootstrapping cluster 
%       components including a highly-available control plane and etcd.}
%     \resumeSubSubItem
%       {Self updating GitHub README; created using Python and GitHub Actions. For this I wrote a custom Python module 
%       `write2list` to convert a Tuple to a List for self-learning purposes.}
%   \resumeSubHeadingListEnd

  \end{document}